Test_code

### 2016-08-22 code/HumanCdGF_microbiota_predict_by_day.Rmd

# read in files
meta_file   <- read.table('../data/process/human_CdGF_metadata.txt', sep = '\t',
                        header = T)
shared_file <- read.table('../data/process/human_CdGF.an.unique_list.0.03.subsample.shared',
                          sep='\t',header = T)
tax_file <- read.table('../data/mothur/gf_cdiff.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.an.unique_list.0.03.cons.taxonomy',
                       sep='\t',header = T, row.names = 'OTU')
# function to label otu with tax
source('tax_level.R')

unused_samples <- c("P2", "CON", "CON2", "CON3")

# remove samples not used or with other cdiff strains
meta_file <- 
  meta_file %>% 
  filter(sample_type == 'stool',
         !cage_id %in% unused_samples) %>% 
  select(Mouse_ID,Group = group, day, cdiff_cfu, Euthanized) %>% 
  mutate(log_cfu = log10(cdiff_cfu + 1)) %>% 
  filter(!is.na(log_cfu))

# create df with day 0 communities with column of mouse_id
day_0_otu_by_mouse <- 
  meta_file %>% 
  filter(day == 0 ) %>% 
  select(Group, Mouse_ID) %>% 
  left_join(shared_file)
day_0_otu_over_01 <- 
  day_0_otu_by_mouse %>% 
  select(contains('Otu')) %>% 
  apply(. , 2, function(i){mean(i)/mean(rowSums(.))}) > 0.01
day_0_otu_over_01 <-  names(day_0_otu_over_01)[day_0_otu_over_01]
day_0_otu_by_mouse_01 <- 
  day_0_otu_by_mouse %>% 
  select(Mouse_ID, one_of(day_0_otu_over_01))

@@

rf_plot_list <- 
lapply(1:10, function(i){
rf_data <- 
  meta_file %>%
  filter(day == i) %>% 
  select(log_cfu, Mouse_ID) %>%
  inner_join(day_0_otu_by_mouse_01) %>% 
  select(-Mouse_ID) %>% 
  tbl_df()

@@

importance_plot_day <- 
  ggplot(data = top_important_OTU, aes(x = factor(OTU), y = Importance)) + 
        geom_point() + scale_x_discrete(limits = rev(top_important_OTU$OTU),
                                        labels = paste(otu_taxa[,1],' (',
                                                       rownames(otu_taxa),')',
                                                       sep='')) +
        labs(x= '', y = '% Increase in MSE') + theme_bw() + coord_flip()

@@

})
```

>>>>

# read in files
meta_file   <- read.table('../data/process/human_CdGF_metadata.txt', sep = '\t',
                        header = T)
shared_file <- read.table('../data/process/human_CdGF.an.unique_list.0.03.subsample.shared',
                          sep='\t',header = T, row.names = 'Group')
tax_file <- read.table('../data/mothur/gf_cdiff.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.an.unique_list.0.03.cons.taxonomy',
                       sep='\t',header = T, row.names = 'OTU')
# function to label otu with tax
source('tax_level.R')

# remove samples not used or with other cdiff strains
meta_file <- 
  meta_file %>% 
  filter(sample_type == 'stool', cdiff_strain == 431) %>% 
  select(Mouse_ID, group, day, cdiff_cfu, Euthanized) %>% 
  mutate(log_cfu = log10(cdiff_cfu + 1)) %>% 
  filter(!is.na(log_cfu))

# create shared with relative abundances over 1%
mean_otu_counts <- unique(apply(shared_file, 1, sum))
rel_abund_shared <- 100 * shared_file / mean_otu_counts
rel_abund_shared_01 <- rel_abund_shared[ , apply(rel_abund_shared, 2, max) > 1]
rel_abund_shared_01$group <- rownames(rel_abund_shared_01)

# create df with day 0 communities with column of mouse_id
day_0_otu_by_mouse <- 
  meta_file %>% 
  filter(day == 0 ) %>% 
  select(group, Mouse_ID) %>% 
  left_join(rel_abund_shared_01)

cfu_by_day <-
  meta_file %>% 
  select(group)

@@

RandomForest_by_day <- function(i, community){
if(community == day_0){
  rf_data <- 
  meta_file %>%
  filter(day == i) %>% 
  select(log_cfu, Mouse_ID) %>%
  inner_join(day_0_otu_by_mouse_01) %>% 
  select(-Mouse_ID)
} else if (community == by_day) {
  rf_data <- 
  meta_file %>%
  filter(day == i) %>% 
  select(log_cfu, Mouse_ID) %>%
  inner_join(day_0_otu_by_mouse_01) %>% 
  select(-Mouse_ID)

} else {
  print('Input for community needed (day_0 or by_day')
}

@@

importance_plot_day <- 
  ggplot(data = top_important_OTU, aes(x = factor(OTU), y = Importance)) + 
        geom_point() + scale_x_discrete(limits = rev(top_important_OTU$OTU),
                                        labels = rev(paste(otu_taxa[,1],' (',
                                                       rownames(otu_taxa),')',
                                                       sep=''))) +
        labs(x= '', y = '% Increase in MSE') + theme_bw() + coord_flip()

@@

})

rf_day_0_comm_plots <- lapply(1:10, day_0)
rf_by_day_com_plots <- lapply(1:10, by_day)
